Source Code Volatility Metric

### 2020-04-19 paper/article.tex
more text

% \documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\documentclass[12pt]{article}
\title{Source Code Volatility Metric}
\author{Yegor Bugayenko}{}{}
% \authorrunning{Yegor Bugayenko}
% \ccsdesc[100]{Software and its engineering~Object oriented languages}
% \keywords{Object-Oriented Programming, Immutability, NCSS}
\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
\usepackage{textcomp}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{total}
\begin{document}
\raggedbottom
\maketitle

\begin{abstract}
A new metric was introduced to calculate the distance
between actively modified files in a source code repository
and the files, which are rarely modified and may be considered
as ``dead'' or ``abandoned.'' It was empirically demonstrated that larger repositories
have larger values of the introduced metric.
\end{abstract}

@@

\section{Related Work}

The metric introduced in this research belongs to the family of
``code change metrics,'' which analyze the history of changes in a repository~\citep{fentonsoftware,choudhary2018}.
Code churn is one of the simplest metric, which counts
all lines being modified (added, edited, and deleted) during
the entire lifetime of a project~\citep{munson1998}. It was demonstrated
by~\citet{shin2010} how code churn, together with complexity and other
developer activity metrics, is related to software vulnerabilities.
The number of changes being made to a particular file, class, method
or line of code is yet another simple metric, used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.

@@

\section{Empirical Results}

@@

\section{Discussion}

@@

\section{Conclusion}

@@

The source code of Ruby and Python scripts used to do the research
is available in GitHub repository \texttt{yegor256/volatility-vs-size}.

\bibliography{main}

>>>>

\documentclass[sigconf]{acmart}
\title{Source Code Volatility Metric}
\author{Yegor Bugayenko}{}{}
\ccsdesc[100]{Software and its engineering~Metrics}
\keywords{Metrics, Software Size, Software Maintainability}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{total}
\begin{document}
\begin{abstract}
A new metric was introduced to calculate the distance
between actively modified files in a source code repository
and the files, which are rarely modified and may be considered
as ``dead'' or ``abandoned.'' It was empirically demonstrated that larger repositories
have larger values of the introduced metric.
The metric may be used for earlier detection of code maintenance anomalies
and helping software developers make the decision of splitting the repository
into smaller oners in order to prevent maintainability issues.
\end{abstract}
\maketitle

@@

The paper is organized as follows.
Section~\ref{sec:background} defines various terms used in the paper.
Section~\ref{sec:related} covers related work in the areas of code change metrics
and empirical analysis of source code repository size.
Section~\ref{sec:method} covers the source code volatility metric.
Section~\ref{sec:results} covers our empirical case study of \thetotalrepos{} Java source code repositories.
Section~\ref{sec:discussion} covers limitations of both the metric and the study.
Finally, we summarize our study in Section~\ref{sec:conclusion}.

\section{Background}
\label{sec:background}

In this paper, we use several terms regarding version control systems and
software metrics. The type of metric we are proposing belongs to the family
of source code change metrics, which analyze the history
of changes in a source code repository~\citep{fentonsoftware,choudhary2018}.
A \emph{change} in a version control system, such as Git, is an individual
modification to the source code file made by a software developer locally
on his/her machine and then \emph{committed} to the repository.

Each version control system, including Git, provides an instrument for
retrieving the entire history of changes from a repository. We use
\texttt{git log} for Git.

\section{Related Work}
\label{sec:related}

The metric introduced in this research belongs to the family of
``code change metrics,''
Code churn is one of the simplest metric in the family, which counts
all lines being modified (added, edited, and deleted) during
the entire lifetime of a project~\citep{munson1998}. It was demonstrated
by~\citet{shin2010} how code churn, together with complexity and other
developer activity metrics, is related to software vulnerabilities.
Yet another simple metrict from the family is
the number of changes being made to a particular file, class, method
or line of code is yet another simple metric, used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.

@@

\section{Empirical Results}
\label{sec:results}

@@

\section{Discussion}
\label{sec:discussion}

@@

\section{Conclusion}
\label{sec:conclusion}

@@

% The source code of Ruby and Python scripts used to do the research
% is available in GitHub repository \texttt{yegor256/volatility-vs-size}.

\bibliographystyle{ACM-Reference-Format}
\bibliography{main}
